\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{multicol}

% Formatting the section and subsection titles
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0pt}{}

% Header setup
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Abdullah Fazli}
\fancyhead[R]{\thepage}

% Custom Itemize Spacing
\setlist[itemize]{left=0pt,itemsep=1pt,topsep=1pt,parsep=0pt,partopsep=0pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Abdullah Fazli}}\\
    (512)-897-2186 \hspace{0.5cm} | \hspace{0.5cm} Austin, Texas \hspace{0.5cm} | \hspace{0.5cm} \href{mailto:abdullahfazli8.af@gmail.com}{abdullahfazli8.af@gmail.com}
\end{center}

\vspace{-1mm}

\section{Education}
\noindent\textbf{Master of Science in Electrical and Computer Engineering: Software Engineering} \hfill \textbf{Spring 2024 - Fall 2025 (CGPA 4.0)}\\
The University of Texas at Austin

\vspace{2mm}

\noindent\textbf{Bachelor of Science in Information Technology} \hfill \textbf{Spring 2019 - Fall 2022 (CGPA 3.6)}\\
The American University of Afghanistan

\vspace{2mm}

\noindent\textbf{Honors and Awards}:
\begin{itemize}
    \item Two President’s High Honor Awards for GPA above 3.7
    \item Two President Honor Awards for GPA above 3.5
\end{itemize}

\section{Technical Skills}
\noindent\textbf{Programming Languages}: 
Python (3 years), C++ (1 year), Java (3 years), JavaScript (3 years), TypeScript (1 year), PHP (Beginner), C (System Programming Knowledge)

\vspace{2mm}

\noindent\textbf{Tech Stack by Activity}:

\begin{itemize}
    \item \textbf{Data Analysis and Machine Learning:}
        \begin{itemize}
            \item Scikit-learn, NumPy, Pandas, Supervised ML, Power BI
        \end{itemize}
    \item \textbf{Web Development:}
        \begin{itemize}
            \item NodeJs, NestJs, VueJs, HTML, CSS, Tailwind, Bootstrap, RESTful APIs, WebSockets
        \end{itemize}
    \item \textbf{Backend Development:}
        \begin{itemize}
            \item MySQL, PostgreSQL, AWS S3, SQL (3 years), Design Patterns (Singleton, Factory, Observer, etc.), JSON Web Token (JWT) for Authentication
        \end{itemize}
    \item \textbf{DevOps and Version Control:}
        \begin{itemize}
            \item GitHub, CI/CD pipelines (GitHub Actions), Docker, Agile Methodology, Documentation (Swagger/OpenAPI)
        \end{itemize}
    \item \textbf{System Programming and Operating Systems:}
        \begin{itemize}
            \item System Programming with C, Windows, Mac OS
        \end{itemize}
\end{itemize}

\vspace{2mm}


\section{Technical Experience}

\subsection*{Arbeiter-Samariter-Bund Deutschland (ASB) \hfill August 2022 – February 2024 (1.5 Years)}
\textit{Backend Software Engineer I}
\begin{itemize}
    \item Architected and developed a comprehensive full-stack clinic management system utilizing \textbf{NestJs} and \textbf{VueJs}, streamlining operations across multiple departments, including patient management, financial tracking, vaccination schedules, and medication administration.
    \item Engineered and optimized key modules to effectively track patients' health data, enabling healthcare providers to securely access patient histories and improve decision-making efficiency.
    \item Led the development of an advanced administrative portal with dynamic reporting capabilities, integrating \textbf{Chart.js} for real-time data visualization, enhancing the ability of clinic administrators to track performance metrics and make data-driven decisions.
    \item Implemented robust \textbf{role-based access control (RBAC)} for secure management of sensitive patient data, ensuring compliance with healthcare privacy standards such as HIPAA, and minimizing unauthorized access to critical information.
    \item Deployed secure authentication mechanisms using \textbf{JWT (JSON Web Tokens)}, providing seamless user login, session management, and data encryption for enhanced security across the system.
    \item Leveraged modern software architecture principles such as \textbf{Model-View-Controller (MVC)}, \textbf{Dependency Injection}, and \textbf{Factory Design Pattern}, ensuring scalability, modularity, and maintainability of the codebase.
    \item Orchestrated automated CI/CD pipelines using \textbf{GitHub Actions}, enabling continuous integration and delivery with a focus on test-driven development, employing \textbf{Jest} for unit testing to ensure high-quality, reliable software releases.
    \item Integrated \textbf{AWS S3} for secure and scalable multimedia storage, utilizing the \textbf{aws-sdk} to efficiently manage and serve patient documents and imaging files, significantly improving system performance and storage scalability.
\end{itemize}


\subsection*{Black Ace Software Solution Company \hfill Dec 2022 – Feb 2022 (3 Months)}
\textit{Software Development Intern}
\begin{itemize}
    \item Spearheaded the development of a full-stack, dynamic website for a goods delivery company, leveraging modern technologies including \textbf{NestJs}, \textbf{MySQL}, \textbf{TypeORM}, and \textbf{Amazon S3} for robust data and media storage management, with \textbf{Vite} to optimize build and development processes.
    \item Engineered the front-end using \textbf{VueJs}, implementing advanced data handling and state management via \textbf{Pinia}, ensuring a smooth user experience and responsive interface.
    \item Integrated secure and scalable authentication mechanisms using \textbf{Auth0}, streamlining login processes and enhancing data protection through industry-standard OAuth2 protocols and JWT-based authorization.
    \item Collaborated in cross-functional Agile teams to design and develop an administrative dashboard enabling real-time management of content and operational data, delivering critical insights for decision-makers.
    \item Implemented a comprehensive authentication system utilizing JWTs for secure API access, incorporating rate-limiting through \textbf{@nestjs/throttler} to prevent brute-force attacks, thereby enhancing security and system resilience.
    \item Established a seamless CI/CD pipeline using \textbf{GitHub Actions}, automating testing (unit tests via \textbf{Jest}) and deployment workflows, significantly reducing manual intervention and accelerating time-to-market.
    \item Managed integration with \textbf{Amazon S3} to store and serve multimedia files efficiently, utilizing advanced cloud storage techniques for scalability and performance optimization.
\end{itemize}


\subsection*{The American University Suleimani Kurdistan \hfill August 2021 – Nov 2022 (1.5 Years)}
\textit{Contract Software Developer for Institutional Effectiveness Department}
\begin{itemize}
    \item Developed a full-stack course assessment system using Django and React.
    \item Automated course review assignments for reviewers based on role-based authentication.
    \item Enhanced data accessibility by transitioning from paper-based reviews to an online platform, improving user satisfaction by 40\%.
\end{itemize}

\subsection*{Eagle Wise Chartered Accountants Company \hfill Jun 2018 – Nov 2018}
\textit{IT Technician}
\begin{itemize}
    \item Provided technical support for hardware, software, and network issues.
    \item Managed IT assets and performed system installations and maintenance.
    \item Assisted in network administration tasks and user account management.
\end{itemize}

\section{Projects}

\subsection*{Robotic Control Implementation using the ATmega328P Microcontroller}
\textit{Overview:} Developed an end-to-end robotic control system integrating multiple sensors and actuators, featuring real-time navigation and collision avoidance capabilities using the \textbf{ATmega328P Microcontroller} and \textbf{C/C++} code. The system was designed to optimize signal processing and feedback control for efficient mechanical hardware management.

\textbf{Key Functions:}
\begin{itemize}
    \item \textbf{Navigation and Collision Avoidance Algorithms:} Designed, simulated, and implemented sophisticated algorithms for real-time navigation, using sensor inputs from multiple sources (Ultrasonic, Infrared, LIDAR, GPS, Accelerometer, Gyroscope) to detect and avoid obstacles.
    \item \textbf{Real-Time Signal Processing and Feedback Control:} Processed real-time data from various sensors to control mechanical functions such as steering and speed through numerical feedback loops.
\end{itemize}

\textbf{Hardware Specifications:}
\begin{itemize}
    \item Microcontroller: \textbf{ATmega328P}
    \item Clock Speed: 16 MHz
    \item RAM: 2 KB SRAM
    \item Signal Sampling Rates: Typically 10-100 Hz based on sensor input
    \item Numerical Precision: 8-bit data processing optimized for performance
    \item I/O Interface: GPIO for sensor inputs and actuator outputs
\end{itemize}

\textbf{Code Implementation and Control Architectures:}
\begin{itemize}
    \item Developed in \textbf{C/C++}, focusing on procedural logic flow, I/O management, and efficient resource handling for real-time signal processing.
    \item Implemented feedback control loops using numerical control architectures, optimizing transient response parameters such as rise time and settling time through second-order transfer functions and feedback compensation.
    \item Utilized discrete transfer functions with numerical poles and zeros to fine-tune the transient response for optimal control over mechanical functions.
    \item Optimized hardware resource management and implemented a scalable architecture for real-time data processing and control.
\end{itemize}

\subsection*{Generative Adversarial Networks (GANs)}
\begin{itemize}
    \item Implemented various GAN architectures (Vanilla GAN, CGAN, WGAN, DCGAN) for image generation.
    \item Used DCGAN with ReLU and Sigmoid functions for high-quality image generation.
\end{itemize}

\subsection*{Library Management System (PHP, SQL)}
\begin{itemize}
    \item Developed a library management system recognized as the winning project at the American University of Afghanistan's IT Day.
    \item Implemented book tracking, PDF uploads, and an administrative dashboard for library operations.
\end{itemize}

\section{Relevant Coursework}
\begin{multicols}{2}
    \begin{itemize}
        \item Statistical Machine Learning
        \item Distributed Systems
        \item Systems Programming
        \item Software Modeling
    \end{itemize}
\end{multicols}

\section{Leadership and Management}
\begin{itemize}
    \item US Consulate and 51Labs Leadership and Entrepreneurship Training Certificate
    \item Managed the 6th annual IT Day at the American University of Afghanistan
\end{itemize}

\end{document}
